Transition to online labs at ECU

### 2020-11-17 2020fallReadingDayECU/survivePivotADI.tex
Changed Trinket to Glowscript in reading day presentation.

{\nologo
  \begin{frame}
    \frametitle{Tools used in online lab delivery}
    \begin{center}
      \renewcommand{\arraystretch}{1.5}
      \begin{tabular}{cll}
        \hline\hline
        \textbf{Tool} & \textbf{Use} & \textbf{Rationale} \\
        \hline
        Canvas & \parbox[t]{2in}{\raggedright Material, Assignments, Quizzes, Discussions,
                 Online Peer Review }& University LMS\\
        WebEx & \parbox[t]{2in}{\raggedright Class introduction, argumentation, group interactions (???)} & University supported\\
        Trinket.io & \parbox[t]{2in}{\raggedright Simulations embedded in Canvas} &
                                                                                    Fine-grained
                                                                                    control\\
        ImageJ &Image processing software &Open-source \\
        Tracker &Video processing software &Open-source \\
        \hline\hline
      \end{tabular}
    \end{center}
  \end{frame}
}

>>>>

{\nologo
  \begin{frame}
    \frametitle{Tools used in online lab delivery}
    \begin{center}
      \renewcommand{\arraystretch}{1.5}
      \begin{tabular}{cll}
        \hline\hline
        \textbf{Tool} & \textbf{Use} & \textbf{Rationale} \\
        \hline
        Canvas & \parbox[t]{2in}{\raggedright Material, Assignments, Quizzes, Discussions,
                 Online Peer Review }& University LMS\\
        WebEx & \parbox[t]{2in}{\raggedright Class introduction, argumentation, group interactions (???)} & University supported\\
        Glowscript.org & \parbox[t]{2in}{\raggedright Simulations embedded in Canvas} &
                                                                                    Fine-grained
                                                                                    control\\
        ImageJ &Image processing software &Open-source \\
        Tracker &Video processing software &Open-source \\
        \hline\hline
      \end{tabular}
    \end{center}
  \end{frame}
}
